\chapter{Discussion}
\label{chap:discussion}

The sensitivity estimates of Section~\ref{sec:sensitivity_comparison} rest on a small set of modelling simplifications that bound their interpretation. The remainder of this chapter addresses the linear-interference omission (Section~\ref{sec:disc_interference}), the single-operator hypothesis (Section~\ref{sec:disc_multi_operator}), the validity of the dimension-eight expansion at high $m_{JJ}$ (Section~\ref{sec:disc_eft_validity}), the absence of systematic uncertainties (Section~\ref{sec:disc_systematics}), and the deferred choice between the three discriminants (Section~\ref{sec:disc_discriminant}).

\section{Interference between the SM and BSM amplitudes}
\label{sec:disc_interference}

The signal samples include only the quadratic EFT term $d^{2}|\mathcal{M}_{8}|^{2}$, while the linear interference term $2d\,\Re(\mathcal{M}_{\mathrm{SM}}^{*}\mathcal{M}_{8})$ is neglected. The quadratic term is positive definite and depends only on the magnitude of the Wilson coefficient, whereas the linear term changes sign with $d$ and must be modelled per operator. The omission is not uniform across the three operator families, since its size tracks the polarisation structure of Chapter~\ref{chap:sm}.

Scalar operators excite only longitudinal modes and therefore share the helicity structure of the SM quartic amplitude, producing the largest linear interference. The quadratic-only model is consequently the least complete on the family with the smallest absolute sensitivity, $Z_A=1.5$ on $S_0$ (Section~\ref{sec:sens_scalar}). Mixed operators lie between the two extremes: their longitudinal component contributes a reduced linear interference, while the transverse component contributes through the quadratic term alone. Tensor operators are orthogonal to the SM amplitude in helicity space, so their linear interference is suppressed. The quadratic-only approximation is therefore most accurate on the family with the largest absolute sensitivity.

\section{Multiple simultaneously active operators}
\label{sec:disc_multi_operator}

Every Asimov significance reported in this thesis is computed under the hypothesis that a single Wilson coefficient is non-zero. A realistic UV completion would generate several non-zero coefficients simultaneously, and the per-operator sensitivities do not combine linearly in that case.

The three discriminants accommodate this scenario unequally. The global binary classifier is trained on all 19 aQGC operators and produces a single output that can be re-used in a multi-coefficient fit without retraining. The specialised classifier covers only the operators in its training pair and is undefined for any other coefficient. The multi-class classifier produces a per-family discriminant output and is, in principle, the natural architecture for disentangling simultaneous activations. The feature ranking and confusion matrices of Section~\ref{sec:multiclass_classification} show, however, that the mixed and tensor softmax nodes are degenerate at the input-feature level. The natural physical handle that would lift this degeneracy is the polarisation of the two reconstructed bosons, since the mixed family produces a transverse-longitudinal final state while the tensor family is purely transverse. Experimental polarisation tagging in the fully hadronic channel is, however, extremely difficult: the boson-decay angles that resolve helicity in leptonic channels are buried in sub-jet observables of the large-$R$ jet, where the calibration and angular resolution are poor and the QCD background is itself anisotropic in the same observables.

A more practical avenue for lifting the family degeneracy, and at the same time for refining the absolute sensitivity, is to include the linear-interference aQGC contribution in the training and evaluation samples instead of the quadratic-only model used here. The linear term itself carries operator-family information that the quadratic term does not, because, as discussed in Section~\ref{sec:disc_interference}, the interference is large for scalar operators, intermediate for mixed operators and strongly suppressed for tensor operators. The shape of the per-bin interference contribution is therefore family-discriminating in its own right, and with quadratic and linear samples in training this family-dependent pattern becomes an additional handle available to the trained network. The same extension removes the quadratic-only restriction of Section~\ref{sec:disc_interference} and yields a more accurate signal model for every operator. Including the linear contribution is therefore the natural next step for the analysis, ahead of any polarisation-tagger development whose experimental feasibility in the fully hadronic channel is far from established.

\section{Validity of the dimension-eight expansion at high invariant mass}
\label{sec:disc_eft_validity}

The amplitude growth $\mathcal{M}_8\propto E^4/\Lambda^4$ is the source of the experimental sensitivity to aQGCs and also of its principal theoretical limitation. The high-$m_{JJ}$ tail that drives the sensitivity lies in the regime where the hierarchy $E\ll\Lambda$ is no longer guaranteed for the Wilson coefficient ranges of interest. Two mitigations are routine in the VBS literature and could be applied on top of the present analysis without altering the training selection or the discriminant choice. The first is a hard energy clipping above a chosen scale $E_{\mathrm{cut}}$, with the unitarity bounds derived in \cite{PhysRevD.101.113003} providing the natural reference. The second is a smooth form-factor reweighting that suppresses the amplitude growth above a chosen scale. Either approach reduces the absolute signal yield in the high-score tail of the discriminant and therefore the reported $Z_A$, with the largest reduction expected on the tensor family whose $E^4$ growth is the steepest.

\section{Remaining systematic uncertainties}
\label{sec:disc_systematics}

The Asimov significances reported in this thesis include a per-bin $30\%$ Gaussian background normalisation uncertainty through Equation~\ref{eq:zasymptotic}. This single-parameter treatment is a conservative envelope of the experimental uncertainty on the QCD multijet background, which contributes more than 90\% of the events in the training selection. The remaining experimental and theoretical uncertainties are not modelled in the present $Z_A$.

The dominant uncertainties not yet treated are the large-$R$ jet energy and mass scale and resolution, which directly distort the input features the discriminant relies on most heavily, and the modelling of the subdominant $V$+jets, $t\bar{t}$ and diboson backgrounds, whose per-process normalisation and shape uncertainties are not separately propagated. On the signal side, the renormalisation and factorisation scales, the parton distribution functions and the parton-shower matching contribute additional uncertainties that propagate as both normalisation and shape distortions. A realistic measurement would profile each of these effects as a separate nuisance parameter, both relaxing the conservative $30\%$ envelope on the QCD multijet component and introducing the smaller, but non-negligible, contributions from the remaining sources.

The three discriminants are not expected to respond identically to a full profiling. The multi-class architecture, whose softmax outputs distribute probability across the four classes, has its sensitivity concentrated in a narrower region of the discriminant score than the binary models, and may consequently shift relative to the binary architectures once the per-process and shape nuisances are introduced.

\section{Choice of final analysis discriminant}
\label{sec:disc_discriminant}

The three architectures occupy distinct trade-offs in the comparison of Section~\ref{sec:sensitivity_comparison}. The specialised classifier reaches the largest absolute $Z_A$ on the scalar and mixed families at the cost of producing three independent networks, each undefined outside its training pair. The global binary classifier loses $29\%$ to $32\%$ of the specialised significance on the scalar family but matches it within $\pm 5\%$ on the mixed family and overtakes it by $17\%$ to $36\%$ on the tensor family, in exchange for a single network that covers the full nineteen-operator basis. The multi-class classifier loses a further $7\%$ to $21\%$ on the tensor family, $31\%$ to $39\%$ on the mixed family and $25\%$ to $27\%$ on the scalar family relative to the specialised model, in exchange for a per-family discriminant whose interpretation as an operator-family identifier becomes useful after the quadratic-plus-linear training extension discussed in Section~\ref{sec:disc_multi_operator}. A definitive choice between the three architectures requires the remaining systematic-uncertainty profiling of Section~\ref{sec:disc_systematics} and a clipping prescription following Section~\ref{sec:disc_eft_validity}, both of which are deferred to the analysis proper. Subject to those studies, the multi-class classifier at the v3 plus equal-$\sigma$ configuration is the preferred architecture of this thesis, since its per-family output becomes a direct operator-family identifier once the linear-interference training extension of Section~\ref{sec:disc_multi_operator} is in place.
