\chapter{Outlook}
\label{chap:outlook}

The sensitivity comparison reported in this thesis is one stage of an analysis that aims to publish constraints on the dimension-eight aQGC Wilson coefficients in the fully hadronic VBS channel. Three steps remain. The signal region must be finalised by tightening the boson-tagger working point and adding an explicit signal-jet mass window (Section~\ref{sec:outlook_signalregion}). The trained discriminant must then be used to set limits on the Wilson coefficients and the result placed in context with the existing measurements (Section~\ref{sec:outlook_limits}). Finally, the analysis is designed as a Run-2 plus Run-3 measurement, and the impact of the Run-3 dataset on the expected reach is discussed in Section~\ref{sec:outlook_run3}.

\section{Finalisation of the signal region}
\label{sec:outlook_signalregion}

The training selection used throughout this thesis (Section~\ref{sec:event_selection}) was chosen to preserve enough background statistics for the MLP to converge while still bringing the phase space close to the analysis signal region. A publishable analysis requires a signal region defined by a tighter set of cuts that enable a data-driven background estimate and that map cleanly onto the three diboson decay channels $WW$, $WZ$ and $ZZ$. Two refinements remain.

\subsection{Boson-tagger working point}
\label{sec:outlook_bosontagger}

The training selection requires DisCoJet${}>0.65$ on both large-$R$ signal jets, which was shown in Section~\ref{sec:event_selection} to outperform the standard tight ATLAS working point of $0.85$ on the dominant tensor operators. The final signal region requires a re-evaluation of this choice under two additional constraints. Firstly, the working point determines the residual QCD multijet contamination, and a final selection must keep this contamination at a level compatible with a data-driven background estimate in the sideband regions. Secondly, the analysis may benefit from splitting the signal region into two or more orthogonal categories defined by different DisCoJet working points, which would expose the boson-decay purity as an additional handle for the profile-likelihood fit. Both choices are decided on the post-fit Asimov significance under the systematic-uncertainty treatment outlined in Section~\ref{sec:disc_systematics}, and not on the statistics-only $Z_A$ used in this thesis.

\subsection{Signal-jet mass window}
\label{sec:outlook_masswindow}

The signal-jet mass is currently an input feature of the MLP discriminant and enters the analysis only implicitly. The final signal region requires an explicit mass window on each large-$R$ jet around the $W$ and $Z$ pole masses, for two reasons. Firstly, an explicit mass window enables sideband-based estimates of the QCD multijet background, which is the dominant uncertainty identified in Section~\ref{sec:disc_systematics}. Secondly, mass windows are the natural way to define $WW$, $WZ$ and $ZZ$ categories, since the $W$ and $Z$ pole masses differ by approximately $10\,\mathrm{GeV}$ and are resolvable in the large-$R$ jet mass distribution. The DisCoJet tagger used in this thesis is explicitly decorrelated from the jet mass, so a mass window can be imposed on top of the tagger output without sculpting the mass distribution in the background. The width of each window is set by the same per-operator Asimov-significance scan that justified the working-point choices in Section~\ref{sec:event_selection}.

\section{Limit setting on the Wilson coefficients}
\label{sec:outlook_limits}

The Asimov significances reported in this thesis are projected onto $95\%$ confidence-level limits on the Wilson coefficients through a profile-likelihood fit to the binned MLP discriminant template. The signal yield in each bin scales as $(f_i/\Lambda^4)^2$ in the quadratic-only model, so the expected limit on a single coefficient scales approximately as $L^{-1/4}$ in the background-limited regime and $L^{-1/2}$ in the signal-limited regime. The fit is repeated for each operator with all others set to zero, and a two-dimensional scan can be performed for any pair of coefficients without retraining the discriminant.

The relevant existing constraints, all from Run-2 data at $\sqrt{s}=13$~TeV, are summarised below. The ATLAS semi-leptonic VBS search \cite{ATLAS:semileptonicVBS:2025} reports $95\%$ CL intervals of $-0.25 < f_{T,0}/\Lambda^4 < 0.22\,\mathrm{TeV}^{-4}$ and $-1.26 < f_{M,0}/\Lambda^4 < 1.25\,\mathrm{TeV}^{-4}$ in $140\,\mathrm{fb}^{-1}$. The CMS semi-leptonic VBS measurement \cite{CMS:semileptonicVBS:2022} uses $138\,\mathrm{fb}^{-1}$ in the $\ell\nu qq$ channel. The fully-leptonic $ZZjj$ channel is covered by ATLAS \cite{ATLAS:fullyleptonicVBS:2024} ($140\,\mathrm{fb}^{-1}$) and CMS \cite{CMS:fullyleptonicZZjj:2021} ($137\,\mathrm{fb}^{-1}$), the latter reporting limits on $f_{T,0}$, $f_{T,1}$, $f_{T,2}$, $f_{T,8}$ and $f_{T,9}$. The ATLAS combination of multiple VBS final states with a triboson measurement \cite{ATLAS:VBStribosoncombination:2026} provides the tightest current limits on a subset of operators by exploiting correlations between channels.

The fully hadronic channel pursued in this thesis carries the largest branching fraction of all VBS topologies, approximately $46\%$ for $WW$, $47\%$ for $WZ$ and $70\%$ for $ZZ$. The corresponding statistical reach therefore complements rather than duplicates the existing leptonic channels, and a future combination of the present analysis with the semi-leptonic and triboson measurements is expected to tighten the per-operator limits beyond what is reachable in any single channel. Such a combination requires consistent EFT-model assumptions across the contributing analyses, in particular the same treatment of the linear interference term discussed in Section~\ref{sec:disc_interference} and a common unitarity-clipping prescription following Section~\ref{sec:disc_eft_validity}.

\section{Impact of the Run-3 dataset}
\label{sec:outlook_run3}

The analysis is designed as a Run-2 plus Run-3 measurement, and the Run-3 dataset is now complete. The LHC Run-3 pp collision programme ran from 2022 to May 2026 at $\sqrt{s}=13.6\,\mathrm{TeV}$ and delivered $332\,\mathrm{fb}^{-1}$ recorded in ATLAS, in addition to the $140\,\mathrm{fb}^{-1}$ collected during Run-2 at $\sqrt{s}=13\,\mathrm{TeV}$. The combined dataset therefore brings the analysis to $472\,\mathrm{fb}^{-1}$, a factor of $3.4$ over the Run-2-only sensitivity studied in this thesis.

The impact on the Wilson coefficient reach depends on the operator. For the high-cross-section tensor operators where the analysis is already in the signal-limited regime (Section~\ref{sec:sens_tensor}), the limit on $f_i/\Lambda^4$ improves approximately as $L^{-1/2}$, giving a roughly $46\%$ tightening from Run-2-only to Run-2 plus Run-3. For the lower-cross-section scalar and mixed operators where the analysis is background-limited, the limit improves as $L^{-1/4}$, giving roughly a $26\%$ tightening. A modest additional improvement is expected from the higher centre-of-mass energy of $13.6\,\mathrm{TeV}$, which raises the VBS cross section by approximately $5\%$ to $10\%$ depending on the diboson final state, and from the improved trigger and pile-up suppression in Run-3 which extends the acceptance into the high-$m_{JJ}$ tail that drives the analysis sensitivity. Combining the Run-3 statistical gain with the channel-combination potential of Section~\ref{sec:outlook_limits} and with the quadratic-plus-linear training extension suggested in Section~\ref{sec:disc_multi_operator} marks the path along which the limits set by this analysis can be pushed substantially below the current single-channel state of the art.
